---
title: "AuthorNet: Expanded Coauthorship Network (Legacy Jusélius Pipeline)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Historical Jusélius Coauthorship Pipeline (Expanded Mode)

*Note: This file is preserved for historical reference and provenance from the original `Juselius_secretdoor` repository. Production analyses should use the generalised modules in `R/` and workflows in `analysis/`.*

## 1. Load Libraries
```{r libraries, eval=FALSE}
library(dplyr)
library(tidyr)
library(igraph)
library(networkD3)
library(openalexR) # or httr queries
library(ggplot2)
```

## 2. Ingest Researcher Cohort
```{r ingest, eval=FALSE}
# Legacy: read names from CSV
authors <- read.csv("legacy_data/juselius_grants_sample.csv", stringsAsFactors = FALSE)
cat("Target authors loaded:", nrow(authors), "\n")
```

## 3. Resolve Authors in OpenAlex & Retrieve Publications (Legacy Heuristic)
```{r openalex, eval=FALSE}
# Legacy approach: Pick candidate with highest works_count (superseded in modern pipeline)
# Query works for each author and collect all coauthorships
```

## 4. Construct Expanded igraph Object
```{r graph, eval=FALSE}
# Edges: shared publications between any author pair in retrieved corpus
# Nodes: target authors + external coauthors
g_expanded <- graph_from_data_frame(edges, directed = FALSE, vertices = nodes)
V(g_expanded)$degree <- degree(g_expanded)
V(g_expanded)$strength <- strength(g_expanded, weights = E(g_expanded)$weight)
V(g_expanded)$betweenness <- betweenness(g_expanded, weights = 1 / E(g_expanded)$weight)
```

## 5. Export Summary
```{r export, eval=FALSE}
# Export netSummary.csv and Gephi GML
write.csv(node_metrics, "legacy_outputs/netSummary.csv", row.names = FALSE)
write_graph(g_expanded, "legacy_outputs/juselius_expanded.gml", format = "gml")
```
